\bf Visualizations for Diagnosing Network Models

### 2019-07-10 paper.Rnw
working on the intro
stuff from last week
just about done but i think it needs some more oomph in the discussion and a bit more connective tissue between sections.

\documentclass[12pt]{article}
% \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
% \geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\usepackage{graphicx}
\usepackage[font=small,skip=5pt]{caption}
\usepackage{subcaption}
\usepackage{animate}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
% \usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{hyperref}
\graphicspath{{figure/}}
\usepackage{endfloat} % Figures to the end of the document

@@

\if0\blind
{
  \title{\bf Visual Diagnostics of Dynamic Social Network Models}
  \author{Sam Tyner \hspace{.2cm}\\
    Department of Statistics and Statistical Laboratory, Iowa State University\\
    and \\
    Heike Hofmann\\
    Department of Statistics and Statistical Laboratory, Iowa State University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visual Diagnostics of Dynamic Social Network Models}
\end{center}
  \medskip
} \fi

>>>>

\documentclass[12pt]{article}
% \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
% \geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\usepackage{graphicx}
\usepackage[font=small,skip=5pt]{caption}
\usepackage{subcaption}
\usepackage{animate}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
% \usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{hyperref}
\graphicspath{{figure/}}
%\usepackage{endfloat} % Figures to the end of the document

@@

\if0\blind
{ % new title ideas: Dynamic Social Network models and their Visualizations
  %                  Visualizations for Diagnosing Network Models  
  \title{\bf Visualizations for Diagnosing Network Models}
  \author{Sam Tyner \hspace{.2cm}\\
    Department of Statistics and Statistical Laboratory, Iowa State University\\
    and \\
    Heike Hofmann\\
    Department of Statistics and Statistical Laboratory, Iowa State University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Visualizations for Diagnosing Network Models}
\end{center}
  \medskip
} \fi
